\documentclass[12pt]{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{adjustbox}
\usepackage{url}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage{natbib}
\usepackage{pdfpages}
\usepackage[raggedright]{ragged2e}
\usepackage[hidelinks]{hyperref}
\usepackage[letterpaper,margin=1in]{geometry}
\bibliographystyle{apsr}   % or plainnat, chicago, apa, etc.
\setcitestyle{authoryear,open={(},close={)},aysep={ }}

\title{We Don't Do That: National Identity and Nuclear Non-Use} 
\author{Wyatt King}
\date{Draft Sections: February 6}

\begin{document}

\maketitle


\section{Introduction}
In his Nobel Prize lecture, Thomas \citet{schelling_astonishing_2006} identified “the most spectacular event” of the late twentieth century as one that did not occur. “We have enjoyed sixty years without nuclear weapons exploded in anger,” he said, “Can we make it through another half dozen decades?”

At the time Schelling gave his speech, burgeoning scholarship argued that a taboo had developed around nuclear weapons during the Cold War, making their use “unthinkable” by its end \citep{tannenwald_stigmatizing_2005, paul_nuclear_1995}. While scholars of the taboo primarily couched their argument in elite-level case studies, they extended it to public opinion, suggesting that it too exhibited a widespread aversion to the use of nuclear weapons. Over the last ten years, a new generation of scholarship on the taboo has challenged this view by fielding survey experiments in which respondents are asked how strongly they would support the first-use of nuclear weapons in different hypothetical scenarios. Consistently, these surveys have found that a majority of respondents in Western, nuclear-armed states would support a first-strike nuclear attack \citep{sagan_revisiting_2017, haworth_what_2019,allison_under_2022, dill_kettles_2022}.

Although these surveys provide robust evidence that the public's aversion to the use of nuclear weapons is not absolute, they do not dismiss that there is a norm against it. All else being equal, people prefer using conventional weapons to nuclear ones and sizable portions of public opinion still strongly oppose using nuclear weapons even when they may be strategically useful \citep{press_atomic_2013}. Consequently, if it is true that the public possesses a normative aversion to the use of nuclear weapons, then what factors can reify this norm and expand its effect?

To answer this question, I return to initial theorizing on the nuclear taboo and argue that people's conceptions of their state's national identity may be one such factor. Following from constructivist theory, I assume that states pursue patterns of behavior that cohere with their self-perceived identities \citep{tannewald_nuclear_2007,wendt_social_1999}. Crucially, these identities can be constructed such that they disqualify certain actions as being beyond the pale--so opposed to a state's national identity as to be antithetical to its interests.

To test whether norms have such "constitutive effects," I field an online survey experiment of Indian citizens similar to those pioneered by Scott Sagan and Benjamin Valentino. Exposing respondents to a hypothetical scenario in which India launches a preemptive counterforce attack against Pakistan, I test how national identity-based arguments opposing nuclear use change the degree of public approval for the attack. Furthermore, considering that the institutionalization of norms may affirm people's conceptions of national identity as being opposed to nuclear use, I gauge how informing respondents of India's No First Use policy changes public support for nuclear use both independent of national identity based arguments and in conjunction with them.

Ultimately, the purpose of this thesis is twofold. Narrowly, it contributes to the upswell of survey experiments from the past ten years, in which scholars have sought to understand what factors impact public support for the use of nuclear weapons. It does so by interrogating the effects that national identity and institutionalization can have, and whether those effects are significant in the manner that scholars of the taboo suggest. More broadly, it seeks to evaluate claims in constructivist literature that norms can have a "constitutive effect," in which people's foreign policy preferences are impacted by their impression of state identity.

[DISCUSSION OF RESULTS]

\section{Literature Review}

What is the nuclear taboo and how does it operate? 

The nuclear taboo can broadly be understood as ``the de facto prohibition against the first use of nuclear weapons'' \citep[10]{tannewald_nuclear_2007}. This prohibition stems from a widespread, moral revulsion to the use of nuclear weapons, which developed during the Cold War and was fully consolidated by its end. A taboo is different from a norm because breaching it is ``unthinkable'' and constitutes crossing a ``bright red line.'' Breaking the nuclear taboo is not only something that states avoid doing, as they might eschew deliberately killing civilians, but it is even ``unimaginable.''

Although scholars of the taboo primarily relied on elite-level case studies in making their argument, they extended it to the public, suggesting that it too displays an aversion to nuclear use. \citet{tannewald_nuclear_2007}  highlights how surveys asking respondents to reflect on the U.S.'s bombings of Hiroshima and Nagasaki have shown a steady decline in approval since the 1940s.\footnote{See \citet{sagan_revisiting_2017} for a condensed overview of this polling.} Moreover, polling conducted concurrently with various conflicts suggest that there was broad public opposition to nuclear weapons use. Before the first Gulf War, for example, more than 75\% of respondents opposed using nuclear weapons should the war have become a stalemate, and a slim majority of respondents opposed the use of nuclear weapons even if Iraq attacked American troops with chemical or biological weapons (CNN/Time Magazine 1990).

Over the last ten years, a second generation of taboo research has been published, challenging whether such an aversion to nuclear use exists today. Focusing on methodological innovations instead of theoretical ones \citep{smetana_forum_2021}, new research has employed survey experiments to evaluate the extent of public support for a first strike nuclear attack in various hypothetical scenarios. \citet{sagan_revisiting_2017} notably simulated what they argue is a modern-day equivalent of the U.S.'s bombings of Japan. Contending that polling Americans about their retrospective preferences for nuclear use during World War II does not adequately prime them to think about the trade-offs of restraint, they presented respondents with a scenario in which the U.S. dropped an atomic bomb on Iran's second largest city to end a ground war that would otherwise kill 20,000 American troops. Despite respondents being told such an attack would kill two million Iranian civilians, 60\% of people approved of it.

Following the publication of these findings, similar studies have since been released affirming that large swaths—if not outright majorities—of the Western public would approve of the first-use of nuclear weapons in different hypothetical scenarios \citep{aronow_note_2019,haworth_what_2019, dill_kettles_2022,schwartz_when_2024}. As these studies have proliferated, the scope of debate has expanded beyond whether there is a nuclear taboo to what factors impact how strongly the public supports nuclear use. Broadly, scholars have focused on three considerations in answering this question: The military and strategic utility of a nuclear attack, states' legal obligations under international law, and the number of civilian casualties incurred by an attack.

\textit{Military and Strategic Utility} Among the first considerations that Sagan and Valentino entertained in their on-going effort to ascertain what factors affect public preferences for nuclear use was the military and strategic utility of an attack. Together with Daryl Press, they argue that the public overwhelmingly—though not exclusively—follows a utilitarian logic of consequences in weighing whether to support nuclear use \citep{press_atomic_2013}. According to the logic of consequences, people's support for nuclear use is predicated on their perceptions of the combined short- and long-term advantages of nuclear weapons as compared to conventional ones. By the military utility of an attack, Press, Sagan, and Valentino refer to the immediate battlefield advantages conferred by atomic weapons use. Should a nuclear bomb destroy an enemy or their infrastructure more substantially, with greater certainty, and while better mitigating domestic casualties than conventional arms, then people will be more inclined to support their use.

By the strategic utility of an attack, the authors refer to the long-run disadvantages tied to setting a new precedent for nuclear use. As Paul (2009) argues, nuclear non-use can be understood as an iterated prisoner's dilemma. On any one battlefield, it may be in a state's interests to defect and use nuclear weapons, but doing so incentivizes an adversary to do the same in a future conflict. As a result, nuclear use may not be desirable because of how it changes opponents' utility functions during future crises. According to this formulation, the apparent norm against nuclear use does not stem from moral reasoning but is the product of coordination, either implicit or explicit, between nuclear-armed states to achieve a mutually beneficial outcome.

Survey experiments have consistently shown that military and strategic calculations exert a powerful influence on the public's willingness to support nuclear weapons use. When a state has a nuclear-armed opponent, the public is far less willing to use nuclear weapons than in asymmetric dyads \citep{haworth_what_2019,allison_under_2022, smetana_moscow_2022}. Holding the opponent constant, support for nuclear use increases dramatically with the chance of success relative to conventional weapons \citep{press_atomic_2013}. To test whether the strategic utility of an attack impacts public preferences for nuclear use, \citet{sagan_atomic_2024} replicated their\textit{ Hiroshima in Iran} scenario, but informed respondents that members of the Joint Chiefs of Staff worried that using weapons would set a bad precedent that could ultimately harm American security. In this treatment group, approval of the attack declined by nearly fifteen percentage points. Moreover, this reduction largely held after respondents were informed that other members of the JCS offered a counter-argument.

\textit{International Law}
\noindent
Beyond the military and strategic utility of a nuclear attack, scholars have also considered how international law may limit states' willingness to use nuclear weapons. According to \citet{tannewald_nuclear_2007}, the institutionalization of nuclear non-use through international agreements has cemented the taboo. Tannenwald interprets institutionalization broadly, saying that it spans not only international human rights law (IHL) but also the Nuclear Non-Proliferation Treaty, bilateral anti-ballistic missile agreements, and declared No-First Use policies. In survey experiments, however, scholars have primarily focused on how IHL can stem support for norm-breaking behavior.

According to the logic of consequences, international law may impact public opinion if people believe that, by breaking it, their state will face material repercussions for their actions. Because international law lacks an enforcement mechanism, though, \citet{sagan_does_2020} argue that it likely has little effect on public attitudes toward nuclear use. Others, however, have argued that international law may have an effect on state behavior if states follow a logic of appropriateness rather than one of consequence. According to the former, states are rule followers who, though not obligated to behave in a given manner, do so anyways to validate a social identity that they have constructed (Fearon and Wendt 2002). According to this thinking, states are not strictly security seekers as neorealists suggest. Rather, they are bound by an informal set of ideas and norms for how states similar to them are expected to behave. 

Outside of nuclear use, surveys have found that the American public is reluctant to support actions knowing that they violate international law \citep{chilton_laws_2014, kreps_flying_2014}. \citet{carpenter_stopping_2020}, replicating a scenario from \textit{Hiroshima in Iran} in which the U.S. uses conventional weapons in a saturation bombing, find that respondents' support for the bombing declines after they are informed that it violates international law. \citet{sagan_does_2020} respond, however, by pointing out that the effect size of informing people about international law is relatively small and easily reversible. Replicating Carpenter and Montgomery's research design, they found that while a minority of respondents approved of the saturation bombing after being informed of it violating international law, only slightly less than 50\% actually did. In a follow up looking at nuclear use, \citet{sagan_atomic_2024} note that if there was disagreement among the Joint Chiefs of Staff regarding the legality of a strike, the initial effect of telling people was attenuated to the point that the difference in support across the treatment and control groups was not statistically significant.


\textit{Civilian Casualties and Moral Frameworks}
\noindent
Scholars have considered how the number of civilian casualties may change the extent of support for nuclear use. If it is true that states have internalized a sensitivity to excessive civilian casualties, owing in part to the legacy of aerial bombings during World War II \citep{pinker_better_2011, thomas_ethics_2014}, then it should follow that people would be opposed to a nuclear attack that would cause large-scale, unnecessary violence. On theoretical grounds, \citet{downes_desperate_2006} and \citet{sagan_revisiting_2017} dispute this characterization by arguing that if such a norm exists at all, it is not strong enough to withstand the domestic political pressure that would arise from a costly war. Downes even concludes that democratically-elected governments are more likely to commit violence against civilians because they may be sensitive to the costs of conflict and, thus, more likely to resort to desperate means. Sagan and Valentino, focusing more narrowly on public opinion, make a similar point, arguing that voters are willing to tolerate large-scale violence perpetrated against civilians in the event substantial troop casualties would otherwise occur.

To test whether civilian immunity exerts a constraining influence on nuclear use, \citet{sagan_revisiting_2017} manipulated the number of civilian casualties incurred by a first-strike attack, holding the number of domestic casualties in a would-be ground war constant at twenty thousand. Despite ratcheting the number of expected civilian deaths from one hundred thousand to two million, public approval of the attack decreased by only a fraction of a percentage point. Meanwhile, preference for the nuclear attack over continuing the ground war declined by eight percentage points, a margin that was not statistically significant in their sample.

In response to this finding, \citet{rathbun_greater_2019} argue that there are a diversity of moral frameworks that people may use in evaluating the merits of nuclear use and not strictly a logic of consequence or appropriateness as Press, Sagan, and Valentino initially argued. Using the typology of moral foundations developed by (Graham et al. 2011), they find that people's support for nuclear use changes depending on whether they adopt liberal, non-liberal, or retributive moral frameworks. Based on this typology, Rathbun and Stein subset survey respondents based on whether they had "individualizing foundations," a sensitivity to others' suffering and a concern for equality and fairness, or "binding foundations," which emphasize deference to authority, in-group loyalty, and the subordination of individual rights to the community. Among those who had stronger individualizing beliefs, support for nuclear decreased substantially as civilian causalities rose. That being said, few respondents overall preferred using nuclear weapons to conventional ones as the number of civilian casualties approached one million, in contrast to Sagan and Valentino's earlier findings.

\section{Theory}
Even as evidence accumulates suggesting that there is no taboo against nuclear use among public opinion, there is reason to believe that a norm against it exists in some capacity. \citet{press_atomic_2013} found, for example, that all else being equal, people vastly prefer the use of conventional weapons to nuclear ones. Additionally, in spite of survey experiments creating "tough tests" for the taboo, in which nuclear use would achieve a compelling military or strategic goal, there is still strong opposition to it.

Little experimental work has been done to understand how this norm can become more influential. However, the original scholarship on the nuclear taboo offers some explanations that have yet to be tested in surveys. Specifically, \citet{tannewald_nuclear_2007} distinguishes between norms' regulative and constitutive effects. The former refer to how norms ``constrain exogenously given self interest and behavior, or lead to recalculations by changing the ‘price’ of behavior,'' \citep[~45]{tannewald_nuclear_2007}. In this formulation, consistent with rationalist interpretations of international relations, norms circumscribe states' behavior while not actually impacting what states' interests are. 

Constructivist scholars break down the assumption that states' interests are independent of norms \citep{wendt_social_1999}. Instead, they treat the relationship between norms and interests as endogenous. In this interpretation, states may follow different norms as a means to validate a social identity. \citet{tannewald_nuclear_2007} argues that by the end of the Cold War, the U.S. eschewed using nuclear weapons because it did not cohere with its identity as a ``civilized'' state. Furthermore, during the first Gulf War, American civil and military leaders began explicitly framing the use of nuclear weapons as something antithetical to United States' identity. Then-Chairman of the Joint Chiefs of Staff Colin Powell called using nuclear weapons ``un-American,'' and White House Chief of Staff John Sununu said that it was something, ``we just don't do.''

If it is true that states' conceptions of their identity can limit what type of weapons are understood as being viable options that cohere with their sense of self, then it follows that:

\begin{quote}
\textbf{H1:} Public support for the use of nuclear weapons will decrease as people are exposed to arguments that the use of nuclear weapons is antithetical to their states' national identity.
\end{quote}

Beyond internally held norms, \citet{tannewald_nuclear_2007} argues that the institutionalization of nuclear non-use reifies the taboo. What counts as the institutionalization of the nuclear taboo is diverse, according to Tannenwald. For example, it can take the form of formal disarmament and non-proliferation treaties, testing bans that stigmatize nuclear weapons development, and anti-ballistic missile treaties that legitimize deterrence. 

Up to this point, a handful of survey experiments have looked into how priming survey respondents about international law impacts their support for nuclear use \citep{carpenter_stopping_2020, sagan_does_2020, sagan_atomic_2024}.  Focusing on international law is constructive and contributes to scholarly debates outside of nuclear weapons use regarding its effectiveness in regulating state behavior; however, pursuant Tannenwald's initial theorizing, it is worth considering how other types of institutions affect support for nuclear use. I propose focusing on no-first use policies, specifically. NFUs are unique among types of institutionalized non-use because they are explicit and unilateral. Compared to international law, which does not explicitly ban the use of small-yield tactical nuclear weapons or similarly proportionate nuclear attacks, NFUs do. Moreover, because NFUs are unilaterally declared, they may be more closely associated with one state's identity rather than an international effort to limit nuclear use.

\begin{quote}
\textbf{H2:} Informing people about their state's No First Use policy will decrease support for a first-strike nuclear attack.
\end{quote}

It may also be reasonable to believe that there is an interactive effect between a state's no-first use policy and their national identity. If it is true, as constructivist scholars contend, that states seek to validate social identities within the international system, then declaring a No First Use policy should be one way through which a state can affirm its identity as a responsible nuclear power. The combined effect therefore of informing survey respondents about an NFU and exposing them to pacifistic national identity arguments may be greater than one treatment on its own. As such, I propose the following hypothesis:

\begin{quote}
\textbf{H3:} Informing individuals about their state’s No First Use policy in combination with exposure to pacifistic national identity arguments will reduce support for the use of nuclear weapons more than either treatment alone.
\end{quote}

\section{Research Design [UNREVISED]}

\textit{Empirical Gaps}
\noindent
As survey experiments like those developed by Sagan and Valentino continue to be fielded, there are several empirical gaps that have yet to be filled in the literature. Among the most notable is that overwhelmingly surveys have been conducted in the United Sates, which considering its history as the only state to have used nuclear weapons may undermine efforts to draw broader conclusions regarding the status of international non-use norms. Although there is evidence suggesting that attitudes in Israel, the U.K., and France toward nuclear use are similar to those in the U.S. \citep{dill_kettles_2022}, the dearth of extant surveys conducted outside of Western, nuclear armed states makes drawing system-wide conclusions difficult. \citet{smetana_moscow_2022} found that a majority of Russian respondents would oppose the first use of nuclear weapons against a NATO member, but given NATO's mutual defense clause and its forward positioning of nuclear weapons in Europe, this conclusion is hardly surprising. As of early 2020, \citet{onderco_ideology_2022} found that sweeping majorities of the Dutch and German public opposed the first use of American nuclear weapons stationed on their territory. That being said, this opposition has substantially weakened since Russia's invasion of Ukraine \citep{onderco_hawks_2023}.

In South Asia, some surveys suggest that a majority of respondents would be willing to use nuclear weapons in certain circumstances. \citet{schwartz_when_2024}, for example, found that most Indian respondents would support using a nuclear weapon against a terrorist cell in Yemen plotting to attack India with a dirty bomb. \citet{clary_public_2021} meanwhile found that people in Punjab, Pakistan would strongly support an escalatory versus de-escalatory response to conventional Indian provocation, albeit the authors did not explicitly distinguish between whether such an escalation would be nuclear or conventional. To the author's knowledge, no survey experiment has yet to be conducted in China.

Outside of questions regarding how well existing surveys generalize to other contexts, there are underlying issues with how opposition to nuclear use has been measured. Up to now, surveys have primarily asked respondents how strongly they approve of nuclear use and how strongly they would prefer it to an alternative, such as either a conventional attack or continuing a costly ground war. Although these questions provide for an effective baseline test of whether the public is dissatisfied with nuclear use, they do not directly assess whether elected leaders would face public protest or electoral punishment for using nuclear weapons. Whether people would be less likely to vote for a sitting government or whether there would be mass-mobilization to protest nuclear use are ultimately more important factors to election-seeking politicians than whether the public is strictly disapproving of nuclear use.

To test my hypotheses, I intend to employ a survey experiment in which Indian respondents are presented with a hypothetical crisis between India and Pakistan. The survey will be conducted via Amazon Mechanical Turk because of its cost efficiency relative to other convenience samples. Like other survey platforms in India, MTurk's samples are disproportionately young, male, upper-caste, and wealthy \citep{boas_recruiting_2020}. To assign treatments, I will use a randomized experiment, where respondents are assigned to one of four groups. The control group will receive no information about India's NFU and no arguments condemning nuclear use. One treatment group will receive information about India's NFU but no arguments, and another treatment will read arguments condemning nuclear use but not receive information about India's NFU. Lastly, one treatment group will both be told of India's NFU and read arguments condemning nuclear use.

Drafts of the hypothetical news articles that respondents in each treatment will read are attached in the appendix below. The situation described is consistent with India's Cold Start doctrine and inspired by what security scholars consider to be the most likely case of Indian nuclear first-use \citep{kapur_ten_2008, clary_indias_2019}. Implemented after the Kargil War, Cold Start is Indian military doctrine enabling it to quickly mobilize along the border with Pakistan following a Pakistan-backed terrorist attack. Within a few days, India can then push across the borders with Punjab and Kashmir in an effort either to claim disputed territory of force a favorable compromise in which Pakistan stops sponsoring cross-border terrorism. 

Although India publicly maintains a no first use policy, Christopher Clary and Vipin Narang argue that during such a ground-war India may contemplate launching a first strike nuclear attack. Because India's military is conventionally superior to Pakistan's, the latter may be incentivized to use a small-yield tactical nuclear weapon on the battlefield to hold territory and stop a further Indian incursion. However, given that Pakistan may use a nuclear weapon, India is in turn encouraged to preempt. Fearing retaliation against one of its cities, Clary and Narang argue that India may conduct a counter-force attack, in which it would target Pakistan's nuclear silos, airfields, and missile launchers in an effort to marginalize the chance of a nuclear attack. 

\textit{A priori}, it is difficult to know how successful such an attack would actually be, given uncertainty regarding where Pakistan's nuclear weapons facilities are, how effective its air defenses would be, and a range of other factors. In the article, I note that it is unclear whether all of Pakistan's strategic nuclear weapons have been destroyed, but that Indian government officials speaking on the condition of anonymity believe that there is a low chance of retaliation. I do so as to create a more difficult test for the taboo while not misleading respondents into believing that a counterforce attack would be guaranteed to work. Furthermore, although it is difficult to gauge how many civilians would die in a counterforce attack, I note that the U.N. warns that it is possible hundreds of thousands did. Again, I do so as to not mislead respondents into believing that a counter force attack could be committed with little harm to civilians, even if the extent of that harm is ambiguous.

Within the article, key pieces of information that may affect respondents' support for nuclear use are highlighted in the article title, dek, and pull quotes. Specifically, I emphasize the number of expected casualties, the target of the attack being Pakistan's nuclear weapon facilities, that government officials believe there is little chance of retaliation, and that India launched the attack amid a ground-war with Pakistan.

Across treatment and control groups, the article is identical, except that people assigned to learn about India's no-first use policy read an additional sentence saying that ``the nuclear attack violates long-standing Indian policy that it would never use nuclear weapons unless first attacked with weapons of mass destruction.'' A pull quote in the middle of the article is meant to draw further attention to this fact.

After reading the article, respondents in the control and NFU treatment groups immediately begin answering questions regarding their support for the use of nuclear weapons in the scenario described. People assigned to reading national identity-based arguments, however, are provided three arguments to read criticizing the use of nuclear weapons. Possible arguments that respondents will read are included in the appendix. Broadly, the arguments that I have written are meant to address different aspects of how conceptions of India's national identity impact its foreign policy. Some emphasize India's legacy of non-violence during the nationalist movement, others more explicitly address India's history of advocating for global disarmament, and a third kind emphasize a transcendent identity shared between Indians and Pakistanis. These arguments follow from previous academic literature on how India's strategic culture, national identity, and nuclear weapons policy overlap \citep{hymans_psychology_2006, bajpai_indian_2014}. To decide what survey questions to include in my experiment, I hope to field a short preliminary experiment in which respondents read the vignette and then grade how convincing a randomly assigned article is on a Likert scale. I would then include whatever arguments were graded as the most persuasive in my final experiment. That being said, considering I may lack funding, I may also forgo this trial experiment and use the first three arguments included in the appendix. I would chose these three in particular because they address different aspects of India's history vis-a-vis nuclear weapons and its identity relative to Pakistan.

When it comes to measuring how strongly respondents support the use of nuclear weapons, I intend to follow \citet{sagan_revisiting_2017} and ask respondents two questions: How strongly would they have preferred using nuclear weapons compared to continuing the ground war, and how strongly would they approve of the use of nuclear weapons? Asking respondents the former provides information about what they believe to be reasonable conduct during war. Asking them the latter is a good indication of respondents' willingness to support the prime minister's decision to use nuclear weapons. This level of approval is also politically relevant insofar as respondents should prefer continuing the ground war but still approve of the use of nuclear weapons, then the government likely faces less political risk regardless of public preferences. To further probe the political implications of nuclear use, I intend to ask respondents whether nuclear use would make them more or less likely to vote for the sitting government and whether they would publicly protest the use of nuclear weapons. These questions are meant to be tougher tests for the degree of public outcry to the use of nuclear weapons. 

Note that in keeping with Sagan and Valentino's survey experiments, I intend to use a six-point Likert scale to measure respondents' preference for and approval of nuclear use. On the scale, respondents must either approve or disapprove and cannot indicate that they are unsure or indifferent to the two options. This design mirrors the ``trolley car'' problem, which philosophers use to assess people's moral reasoning when faced with difficult ethical trade-offs \citep{sagan_does_2020}.

In addition to the above, I intend to collect information on potential covariates in a pre-treatment survey administered to respondents. I specifically ask how strongly people approve the Indian National Congress and Bharatiya Janata Party on a seven point Likert scale. These questions will serve as controls for people's political preferences in the regression models described below. I will also ask how strongly respondents agree with the statements that ``India should not use force against another country unless absolutely necessary'' and ``India should never use nuclear weapons unless it is retaliating against another country for using them first.'' Responses to these questions are meant to be highly correlated with their preferences for nuclear use after reading the hypothetical as to reduce standard errors and increase statistical power when I perform my statistical analyses.

To evaluate the support for my hypotheses, I intend to use two statistical procedures primarily. First is a difference of proportions test, comparing people's approval and preference for the nuclear attack between the control and treatment groups. Second is a logistic regression, in which I dichotomize people's approval for nuclear use as the outcome variable and include controls for people's demographics, their political beliefs, and their pre-treatment attitudes toward nuclear use. For robustness, I will also conduct a series of ordinal regressions, using the same independent variables as for the logistic regression.

\section{Findings}

\section{Conclusion}

\bibliography{references}

\end{document}
